\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-08-06 write_up/mixfishsim_ecolmod.tex
Demographic stochasticity

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations. As such, we favoured a
minimum realistic model of the fish populations \citep{Plaganyi2014}, while
incorporating detailed fishing dynamics that take account of different drivers
in a mechanistic way. In this way we take account of heterogeneity in fleet
dynamics due to different preferences and drivers similarly to other approaches
\citep{Fulton2011}, but at an individual vessel rather than fleet level. We do
not explicitly define fleets as rational profit maximisers at the outset, but
consider there are several stages to development of the fishery; information
gathering through search where the resource location is not known,  followed by
individual learnt behaviour of profitable locations.  This provides a realistic
model of how fishing patterns are established and maintained to exploit an
uncertain resource through an explore-exploit strategy \citep{Mangel1983,
	Bailey2018}.

>>>>

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations. As such, we favoured a minimum
realistic model of the fish populations \citep{Plaganyi2014} taking account of
environmental but not demographic stochasticity, while incorporating detailed
fishing dynamics that take account of different drivers in a mechanistic way.
\\

Demographic stochasticity arises due to individual-level variability in time to
reproduction and death. This form of stochasticity is often modelled by drawing
random time intervals from a given distribution \citep{Gillespie1977}. The
impact of demographic stochasticity depends on the population size, with the
effects expected to decrease with increasing population size \citep{Lande2010}.
This contrasts with environmental stochasticity, which affects all population
sizes and is present at the population level in our model by variability in
recruitment. \\

We take account of heterogeneity in fleet dynamics due to different preferences
and drivers similarly to other approaches \citep{Fulton2011}, but at an
individual vessel rather than fleet level. We do not explicitly define fleets
as rational profit maximisers at the outset, but consider there are several
stages to development of the fishery; information gathering through search
where the resource location is not known, followed by individual learnt
behaviour of profitable locations.  This provides a realistic model of how
fishing patterns are established and maintained to exploit an uncertain
resource through an explore-exploit strategy \citep{Mangel1983, Bailey2018}.
